Hydras \& Co.

### 2022-03-25 doc/part-hydras.tex
minor improvements

We prove this lemma by transfinite induction on $\alpha$.
Let us consider a path $\alpha \xrightarrow [i]{} \beta$ $(i>0)$. Its first step is
the pair $(\alpha,\canonseq{\alpha}{i})$, We have $\canonseq{\alpha}{i}<\alpha$ and
$\canonseq{\alpha}{i} \xrightarrow [i]{} \beta$. 
Let $n$ be any natural number such that $n>i$.
By the induction hypothesis, there exists a path $\canonseq{\alpha}{n} \xrightarrow[i]{} \beta$.
\begin{itemize}
\item  If $\alpha$ is a successor ordinal $\gamma+1$, then $\canonseq{\alpha}{n} =
\canonseq{\alpha}{i}=\gamma$. Thus we have a path 
$\alpha  \xrightarrow [n]{}  \gamma \xrightarrow [n]{} \beta$
\item If $\alpha$ is a limit ordinal, we apply the following theorem (numbered \texttt{2.4} in Ketonen and Solovay's article).

@@

Intuitively, lemma   \texttt{Lemma2\_6\_1}  shows that if $\beta<\alpha<\epsilon_0$, then there exists  a battle from $\iota(\alpha)$ to $\iota(\beta)$ where the replication factor is constant, although large enough.

 \paragraph*{\gaiasign}
 Corollary \texttt{Cor12} and Lemma \texttt{Lemma261} are also available in
\href{../theories/html/gaia_hydras.GPaths.html}{gaia\_hydras.GPaths} 
(please see Sect.\~ref{sect:gpath}).

>>>>

First, let us prove the following lemma (numbered \texttt{2.4} in Ketonen and Solovay's article).

We prove this lemma by transfinite induction on $\alpha$.
Let us consider a path $\alpha \xrightarrow [i]{} \beta$ $(i>0)$. Its first step is
the pair $(\alpha,\canonseq{\alpha}{i})$, We have $\canonseq{\alpha}{i}<\alpha$ and
$\canonseq{\alpha}{i} \xrightarrow [i]{} \beta$. 
Let $n$ be any natural number such that $n>i$.
By the induction hypothesis, there exists a path $\canonseq{\alpha}{n} \xrightarrow[i]{} \beta$.
\begin{itemize}
\item  If $\alpha$ is a successor ordinal $\gamma+1$, then $\canonseq{\alpha}{n} =
\canonseq{\alpha}{i}=\gamma$. Thus we have a path 
$\alpha  \xrightarrow [n]{}  \gamma \xrightarrow [n]{} \beta$
\item If $\alpha$ is a limit ordinal, we apply Theorem \texttt{KS\_thm\_2\_4} (see above).

@@

Intuitively, Lemma~\texttt{2\_6\_1}  shows that if $\beta<\alpha<\epsilon_0$, then there exists  a battle from $\iota(\alpha)$ to $\iota(\beta)$ where the replication factor is constant, although large enough.

 \paragraph*{\gaiasign}
 Corollary \texttt{Cor12} and Lemma \texttt{Lemma2\_6\_1} are also available in
\href{../theories/html/gaia_hydras.GPaths.html}{gaia\_hydras.GPaths} 
(please see Sect.~\vref{sect:gpath}).
